\chapter*{Preface\markboth{Preface}{Preface}}\label{ch:preface}
\addcontentsline{toc}{chapter}{Preface}

This report was written by CS-23-SW4-01, a group of students in the fourth semester of studying Software at Aalborg University. 

\subsubsection{Code snippets}
The report contains code snippets. In some snippets, parts of the code that are less relevant to the points being made have been omitted. This is indicated with [. . .] as seen in listing \ref{list:CodeSnippetExample}.

\begin{lstlisting}[language = csharp, firstnumber=1, label={list:CodeSnippetExample},caption=Example of the structure of a code snippet. Lines 2-4 indicate omitted code]
//First part of code snippet
.
.
.
//Continuation of the code snippet
\end{lstlisting}

\subsubsection{Target audience}
The target audience for this project is computer science students at the beginning of their fourth semester. The target group for the product is high school students who are learning programming for the first time. 

\subsubsection{Application of theory}
The report is structured in a way so that the necessary theory for a section or subsection is presented to the reader at the start of the section. Subsequently, the theory will be applied in a way that assumes the reader understands it.   

\subsubsection{Acknowledgements}
We would like to express our gratitude to our supervisor Lone Leth Thomsen for her guidance and support throughout the project. Furthermore, we would like to thank Morten Konggaard Schou for assisting us with the semantic definitions for \lang.  


\newpage

\vspace{\baselineskip}\hfill Aalborg University, \today
\vfill\noindent
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.5pt}\\
  Charlotte Sundahl Elleby\\
 {\footnotesize <celleb21@student.aau.dk>}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.5pt}\\
  Christian Povlsen\\
 {\footnotesize <cpovls21@student.aau.dk>}
\end{minipage}
\vspace{3\baselineskip}
\hfill
\vfill\noindent
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.5pt}\\
  Nichlas Seerup Hjorth\\
 {\footnotesize <nhjor21@student.aau.dk>}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.5pt}\\
  Rasmus Bartholomay Vikøren Borup\\
 {\footnotesize <rborup21@student.aau.dk>}
\end{minipage}
\vspace{3\baselineskip}
\hfill
\vfill\noindent
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.5pt}\\
  Thomas Bjeldbak Madsen\\
 {\footnotesize <tbma21@student.aau.dk>}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.5pt}\\
  Thomas Ilum Andersen\\
 {\footnotesize <tian21@student.aau.dk>}
\end{minipage}
\vspace{3\baselineskip}
\hfill


